---
title: "Subsetting out the inital training and holdback data sets"
subtitle: "NLP for Tile and Abstract Screening as part of a literature review extracting diversity changes over space and time"
author: '[Dominique Maucieri](https://www.dominiquemaucieri.com)'
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    toc: yes
    toc_depth: 4
editor_options: 
  markdown: 
    wrap: 72
---

# Environment setup

```{r setup, include=FALSE}
#run this chunk to set up the environment to run the rest of the code

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, tidy = TRUE, message=FALSE)

#To clear the workspace
rm(list = ls(all = T))

# Packages
library(here)

```


# Creating initial training data set

This code will only be run once to extract and export the training data set for manual classification in Covidence


```{r}
#parameters
number_of_training_samples <- 100
number_of_holdout_samples <- 100
```


# Combining dataset and removing duplicates

**code if needed


# Subsetting


Code randomly subsets the `number_of_training_samples` and `number_of_holdout_samples` as specified above and then saves the first portion as covidence training samples and the second portion as the holdout training set. 

Code retains the RIS formatting needed to upload to Covidence

```{r}
# creating training set
example_references <- readLines(here("05_archived_examples/example_nlp" ,
                                    "wos_download_full.ris"), warn = FALSE)

all_references <- example_references

# all_references <- readLines(here("01_data/inital_raw_database_downloads" ,
#                                     "wos_download_full.ris"), warn = FALSE)

end_of_sample_indices <- which(all_references == "ER  -")

all_papers <- list()
start_idx <- 1

for (end_idx in end_of_sample_indices) {
  all_papers[[length(all_papers) + 1]] <- all_references[start_idx:end_idx]
  start_idx <- end_idx + 1
}

set.seed(756)
training_and_holdout_samples <- sample(all_papers, 
                           size = number_of_training_samples + number_of_holdout_samples,
                           replace = FALSE)

training_samples <- training_and_holdout_samples[1:number_of_training_samples]


training_output_lines <- unlist(training_samples)

writeLines(training_output_lines, 
           con = here("01_data/initial_to_be_classified",
                      "unclassified_initial_covidence_training.ris"), useBytes = TRUE)


holdout_samples <- training_and_holdout_samples[(number_of_training_samples +
                                                   1):(number_of_training_samples + 
                                                         number_of_holdout_samples)]

holdout_output_lines <- unlist(holdout_samples)

writeLines(holdout_output_lines, 
           con = here("03_holdout_data/to_be_classified",
                      "unclassified_holdout_samples.ris"), useBytes = TRUE)


```
